Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-09-28 bd_notation.tex
[review] 1. Radii in fig. 6 indicated. 2. Typo fixed and definition added for the Hurwitz calculation 3. Redundant equations removed and reference to them added 4. Fig 7-10, the legend for error bar modified. (a) and (b) added
[review] Some texts changed

We use chemical reaction style to represent the change of boundary conditions. Taking the example of the echo diagrams in Fig.~\ref{fig:echo}, there are three boundary conditions $a,b,c$ in the folding picture, which represents the status on two ends of the chain before and after the quench. The choice of a uniform $c$ boundary condition on the far end of the chain is to isolate the effect coming from the bcc on the conformal interface. The process $a + c \rightarrow b + c$ represents the change of boundary condition from the combination $a$/$c$ prior the quench to $b$/$c$ after the quench. Since each letter can take a general conformal interface defined by the $S$ matrix in Eq.~\eqref{eq:S1_S2}, we denote it as
\begin{equation}
S_a( \theta_a ) + S_c( \theta_c) \rightarrow S_b( \theta_b )  + S_c( \theta_c ) .
\end{equation}
Analytic computation can be performed when we neglect the boundary condition $c$, assuming $L \gg \tau$. To remove the bcc operator from $c$ to $a$ at infinity, we take $a = c$ in the numerical calculation.

In the ``cut-and-join" protocol we considered, $a$ should be one of `DD', `DN', `ND', `NN', $b$ is taken to be $S_1( \theta )$ or $S_2( \theta )$. The physical situation of connecting two compact bosons (and our numerical simulation) corresponds to the choice of $S_1( \theta)$, and we reserve the notation $\lambda$ for this type of boundary condition. For instance, the notation for the process presented in Fig.~\ref{fig:echo} is
\begin{equation}
{\rm DN }  + {\rm DN} \rightarrow \lambda + { \rm DN} .
\end{equation}
Another interesting case is to take $a$ or $c$ to be completely transmitting interface, i.e. $S_2( \frac{\pi}{4} )$. This S-matrix corresponds to the traditional periodic boundary condition and we use symbol 'P' to denote it.

>>>>

We use chemical reaction style to represent the change of boundary conditions. Taking the example of the echo diagrams in Fig.~\ref{fig:echo}, there are three boundary conditions $a,b,c$ in the folding picture, which represents the status on two ends of the chain before and after the quench. The choice of a uniform $c$ boundary condition on the far end of the chain is to isolate the effect coming from the bcc on the conformal interface. The process $a + c \rightarrow b + c$ represents the change of boundary condition from the combination $a$/$c$ prior the quench to $b$/$c$ after the quench. Since each letter can take a general conformal interface defined by the $S$ matrix in Eq.~\eqref{eq:S1_S2}, we denote it as
\begin{equation}
S_a( \theta_a ) + S_c( \theta_c) \rightarrow S_b( \theta_b )  + S_c( \theta_c ) .
\end{equation}
{\color{red} Analytic computation can be performed when we neglect the boundary condition $c$, assuming $L \gg \tau$. To remove the bcc operator from $c$ to $a$ at infinity, we take $a = c$ in the numerical calculation. Probably changed to: To remove the bcc operator from c to a at infinity, the analytic and numerical calculations are performed by taking $a=c$ and $L\gg\tau$.}

In the ``cut-and-join" protocol we considered, $a$ should be one of `DD', `DN', `ND', `NN', $b$ is taken to be $S_1( \theta )$ or $S_2( \theta )$. The physical situation of connecting two compact bosons (and our numerical simulation) corresponds to the choice of $S_1( \theta)$, and we reserve the notation $\lambda$ for this type of boundary condition. For instance, the notation for the process presented in Fig.~\ref{fig:echo} is
\begin{equation}
\label{eq:DNDN}
{\rm DN }  + {\rm DN} \rightarrow \lambda + { \rm DN} .
\end{equation}
Another interesting case is to take $a$ or $c$ to be completely transmitting interface, i.e. $S_2( \frac{\pi}{4} )$. This S-matrix corresponds to the traditional periodic boundary condition and we use symbol 'P' to denote it.

### 2017-09-28 general_formulation.tex
[review] Some texts changed

The physical significance of $\theta$ will be clear in the scattering process described below. We rewrite Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and use $\partial_{\pm} = \partial_{t} \pm \partial_x $ to extract the left and right going modes. For example, $\partial_{-} \phi^2$ will be a function of $t - x$ and hence represents a right going mode on the right half plane. This mode is one of the scattering modes that leave the interface. On the other hand $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approach the interface from their respective domain. We therefore establish the scattering relation 
\begin{equation}\begin{aligned}
\label{eq:def_S}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix},
\end{aligned}\end{equation}
and solve the $S$ matrix for the two cases of $M_1$ and $M_2$
\begin{equation}\begin{aligned}
\label{eq:S1_S2}
S_1(\theta)=\begin{bmatrix}
\cos 2\theta & \sin 2\theta \\
\sin 2\theta & -\cos 2\theta
\end{bmatrix},\
S_2(\theta)=\begin{bmatrix}
-\cos 2\theta & \sin 2\theta \\
-\sin 2\theta & -\cos 2\theta
\end{bmatrix}.
\end{aligned}\end{equation}
For generic values of $\theta$, the interface is partially-transmitting, whose transmission and reflection coefficients can be read off from the scattering matrices. We note that the S-matrices are independent of the wavelength, which agrees with the fact that the interface is scale invariant. 
\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{fig_folding_pic.pdf}
\caption{Folding picture for the penetrable interface. Left panel: World line of the penetrable interface. $\partial_\pm\phi^{1,2}$ denote the left and right going modes in their respective domains. Right panel: Folding operation that sends $\phi^2(x)$ to $\phi^2(-x)$. The dashline represents the \emph{im}penetrable boundary for the resulting tensor theory. The arrow represents the incoming and outgoing particle scattered by the interface.}
\label{fig:folding_pic}
\end{figure}

>>>>

The physical significance of $\theta$ will be clear in the scattering process described below. We rewrite Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and use $\partial_{\pm} = \partial_{t} \pm \partial_x $ to extract the left and right going modes. For example, $\partial_{-} \phi^2$ will be a function of $t - x$ and hence represents a right going mode on the right half plane. This mode is one of the scattering modes that leave the interface. On the other hand $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approach the interface from their respective domain. We therefore establish the scattering relation 
\begin{equation}\begin{aligned}
\label{eq:def_S}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix},
\end{aligned}\end{equation}
and solve the $S$ matrix for the two cases of $M_1$ and $M_2$
\begin{equation}\begin{aligned}
\label{eq:S1_S2}
S_1(\theta)=\begin{bmatrix}
\cos 2\theta & \sin 2\theta \\
\sin 2\theta & -\cos 2\theta
\end{bmatrix},\
S_2(\theta)=\begin{bmatrix}
-\cos 2\theta & \sin 2\theta \\
-\sin 2\theta & -\cos 2\theta
\end{bmatrix}.
\end{aligned}\end{equation}
For generic values of $\theta$, the interface is partially-transmitting, 
{\color{red}whose transmission coefficient
%and reflection coefficients 
can be read off from the scattering matrices
\begin{eqnarray}\begin{aligned}
t = \sin2\theta.
\end{aligned}\end{eqnarray}
}
We note that the S-matrices are independent of the wavelength, which agrees with the fact that the interface is scale invariant. 
\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{fig_folding_pic.pdf}
\caption{Folding picture for the penetrable interface. Left panel: World line of the penetrable interface. $\partial_\pm\phi^{1,2}$ denote the left and right going modes in their respective domains. Right panel: Folding operation that sends $\phi^2(x)$ to $\phi^2(-x)$. The dashline represents the \emph{im}penetrable boundary for the resulting tensor theory. The arrow represents the incoming and outgoing particle scattered by the interface.}
\label{fig:folding_pic}
\end{figure}

### 2017-09-28 num_result.tex
[review] Some texts changed

Finally, we also provide the data for the process
\begin{equation}
\label{eq:DNP_rand()}
{\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P},
\end{equation}
to evaluate the influence of the boundary condition $c$. It {\rm does} influence the scaling dimension, which is not captured by our analytic calculation. Specifically, the large value of $\theta$ still follows the quadratic relation with a deficit of $\frac{1}{8}$, while the small $\theta$ value has smaller deficit and merge with the analytic curve at $\theta = 0$. 
\begin{figure}[htb]
\centering
\includegraphics[width=1\columnwidth]{PDN_fit.pdf}
\caption{The decay exponent of Loschmidt echo for the process {\color{red}in Eq.~\eqref{eq:DNP_rand()}.} The boundary condition $c$, which is now different from $a$, changes the scaling completely from the analytic quadratic curve. The deficit to the analytic value is roughly $\frac{1}{8}$ for $\theta > \frac{\pi}{4}$, It becomes smaller and approaches zero for small $\theta$. }
\label{fig:PDN_fit}
\end{figure}

>>>>

Finally, we also provide the data for the process
\begin{equation}
\label{eq:DNP_rand()}
{\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P},
\end{equation}
to evaluate the influence of the boundary condition $c$. It {\rm does} influence the scaling dimension, which is not captured by our analytic calculation. {\color{red}Specifically, the large value of $\theta$ still follows the quadratic relation with a deficit of $\frac{1}{8}$, while the small $\theta$ value has smaller deficit and merge with the analytic curve at $\theta = 0$. Probably change to: We note that the exponent still follows the quadratic relation with a deficit of $\frac{1}{8}$ at larger value of $\theta$. The deficit approaches zero at $\theta=0$ where the setups are the same before and after quench.}
\begin{figure}[htb]
\centering
\includegraphics[width=1\columnwidth]{PDN_fit.pdf}
\caption{The decay exponent of Loschmidt echo for the process {\color{red}in Eq.~\eqref{eq:DNP_rand()}.} The boundary condition $c$, which is now different from $a$, changes the scaling completely from the analytic quadratic curve. The deficit to the analytic value is roughly $\frac{1}{8}$ for $\theta > \frac{\pi}{4}$, It becomes smaller and approaches zero for small $\theta$. }
\label{fig:PDN_fit}
\end{figure}
